Distribution-oblivious Programming with Dish

### 2019-11-18 pldi/draft.tex
Teensy update

The combination of automated transformations for program distribution with the ability to maintain correct non-distributed semantics results in several benefits.
% \sys converts legacy shell pipelines into their distributed equivalents fully automatically, offering $100\times$ improvements in performance without a single line of additional code or annotation.
First, shell users composing pipelines (or simply running legacy pipelines on massive datasets) can see scalability benefits without any manual effort---no need for \ttt{qsub}, SLURM, calls to \ttt{parallel}, or any manual rewriting.
Second, developers of new shell commands can use a concise a domain-specific language to express their distributability properties rather than using ad-hoc, command-specific flags such as {\tt t}  \#threads, \ttt{-t}, \ttt{-p} \etc
Most importantly, \sys provides an architectural lesson for system designers---namely that large-scale research efforts in the distributed- and operating-system literature to provide a \unix-like distributed equivalent could have been simplified by a thin (but sophisticated) rewriting shim like the one \sys provides.

>>>>

The combination of automated transformations for program distribution with the ability to maintain correct non-distributed semantics results in several benefits.
% \sys converts legacy shell pipelines into their distributed equivalents fully automatically, offering $100\times$ improvements in performance without a single line of additional code or annotation.
First, shell users composing pipelines (or simply running legacy pipelines on massive datasets) can see scalability benefits without any manual effort---no need for \ttt{qsub}~\cite{gentzsch2001sun}, \textsc{SLURM}~\cite{yoo2003slurm}, calls to \textsc{GNU} \ttt{parallel}~\cite{Tange2011a}, or any manual rewriting~\cite{mapreduce:08, ciel:11, spark:12}.
Second, developers of new shell commands can use a concise a domain-specific language to express their distributability properties rather than using ad-hoc, command-specific flags such as {\tt -t},  \#threads, \ttt{-t}, \ttt{-p} \etc
Most importantly, \sys provides an architectural lesson for system designers---namely, that large-scale research efforts in the distributed- and operating-system literature to provide a \unix-like distributed equivalent~\cite{ousterhout1988sprite, mullender1990amoeba, pike1990plan9, barak1998mosix} would have been simplified by a thin (but sophisticated) rewriting shim like the one \sys provides.
